Discussion

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
changed subjective values to SVs
put 2 sentences into 1

Knowing whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
To establish the *trait* nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020].
The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation. 
By definition, this represents a state.
As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
We believe that these goals, factors, and demands also influence individual SVs of ER strategies.
Our data presented in this study support this idea.
However, this also implies that SVs should differ according to situational factors (e.g. stimulus intensity).
The ER goals that individuals pursue in a given situation must also be taken into account.
In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals[@Tamir2016].
Wilms and colleagues[-@Wilms2020] pointed out that ER goals, as well as situational factors, should be treated as states, because both vary greatly from event to event and situation to situation.
In a different situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, a different strategy might appear more helpful and thus have a higher SV.
It should also be noted that the calculation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also [Limitations](#Limitations)).
Therefore, SVs may vary when different reference strategies are used.
It is conceivable that subjective values are likely to be highly correlated in situations with similar demands and goals. 
They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
Of course, it is also possible that such habits influence the internal formation of these subjective values.
However, our data are not suitable for answering this question.
In the future, SVs should therefore be collected in several similar situations. 
Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being[@GrossJohn2003].

@@

Third, a major limitation is that participants had to use three prescribed ER strategies.
It may be that some of the participants were not used to any of these strategies in everyday life.
So it could be that none of the strategies has a really high subjective value for the person.
However, the strategies selected for attentional deployment, cognitive change, and response modulation have been shown meta-analytically to be most effective[@Webb2012]. 
In this context, the individual SVs of each person must be interpreted with caution. 
They depend on the specific context: The stimuli presented and the strategies compared.
For example, SVs for an ER strategy might be higher or lower when different stimuli or stimulus valences and different comparison strategies are used, because the calculation of SVs is inseparable form the other SVs.

>>>>

Knowing whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
To establish the *trait* nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020].
The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation. 
By definition, this represents a state.
As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
We believe that these goals, factors, and demands also influence individual SVs of ER strategies.
Our data presented in this study support this idea.
However, this also implies that SVs should differ according to situational factors (e.g. stimulus intensity).
The ER goals that individuals pursue in a given situation must also be taken into account.
In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals[@Tamir2016].
Wilms and colleagues[-@Wilms2020] pointed out that ER goals, as well as situational factors, should be treated as states, because both vary greatly from event to event and situation to situation.
In a different situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, a different strategy might appear more helpful and thus have a higher SV.
It should also be noted that the calculation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also [Limitations](#Limitations)).
Therefore, SVs may vary when different reference strategies are used.
It is conceivable that SVs are likely to be highly correlated in situations with similar demands and goals. 
They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
Of course, it is also possible that such habits influence the internal formation of these subjective values.
However, our data are not suitable for answering this question.
In the future, SVs should therefore be collected in several similar situations. 
Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being[@GrossJohn2003].

@@

Third, a major limitation is that participants had to use three prescribed ER strategies.
It may be that some of the participants were not used to any of these strategies in everyday life, so none of the strategies actually had a high subjective value for them.
However, the strategies selected for attentional deployment, cognitive change, and response modulation have been shown meta-analytically to be most effective[@Webb2012]. 
In this context, the individual SVs of each person must be interpreted with caution. 
They depend on the specific context: The stimuli presented and the strategies compared.
For example, SVs for an ER strategy might be higher or lower when different stimuli or stimulus valences and different comparison strategies are used, because the calculation of SVs is inseparable form the other SVs.
